---
title: "Regression 5"
author: "Nam Tran"
format: docx
editor: visual
---

Packages used

```{r}
pacman::p_load(tidyverse, 
               magrittr,
               skimr,
               psych,
               broom)
options(scipen = 999)
```

# Data Preparation

```{r}
full_data <- read.csv('reg2_data.csv', stringsAsFactors = T)

full_data %<>%
  select(-c(X, year)) %>% 
  mutate(PERMNO = as.factor(PERMNO),
         date = ymd(date)
         )
```

1.  Create an adjusted market premium column

```{r}

# Calculate the total market cap of all stocks for each date
full_data %<>%
  group_by(date) %>%
  mutate(Total_Market_Cap = sum(MKT_CAP)) %>%
  ungroup()

# Calculate the adjusted market return for each stock
full_data %<>%
  group_by(date, PERMNO) %>%
  mutate(Adjusted_Market_Cap = Total_Market_Cap - MKT_CAP) %>%
  ungroup()

# Calculate the adjusted market return column
full_data %<>%
  mutate(
    Adjusted_Market_Return = 
      (mkret * Total_Market_Cap - ind_ret * MKT_CAP) / Adjusted_Market_Cap)


# Calculate the adjusted market return premium

full_data %<>%
  mutate(Adj_Market_Ret_Prem = Adjusted_Market_Return - EFFR)
```

2.  Create adjusted sector premium column

```{r}

# Calculate the total market cap of all stocks in a sector for each date
full_data %<>%
  group_by(date, Sector) %>%
  mutate(Total_Sector_Market_Cap = sum(MKT_CAP)) %>%
  ungroup()

# Calculate the unadjusted daily sector return 

full_data %<>%
  group_by(date, Sector) %>%
  mutate(sector_ret = sum(ind_ret*MKT_CAP)/Total_Sector_Market_Cap) %>%
  ungroup()


# Calculate the adjusted sector market cap 

full_data %<>% 
  mutate(Adjusted_Sector_Market_Cap = Total_Sector_Market_Cap - MKT_CAP)


# Calculate the adjusted market return column
full_data %<>%
  mutate(
    Adjusted_Sector_Return = 
      (sector_ret * Total_Sector_Market_Cap - ind_ret * MKT_CAP) / Adjusted_Sector_Market_Cap)


# Calculate the adjusted market return premium

full_data %<>%
  mutate(Adj_Sector_Ret_Prem = Adjusted_Sector_Return - EFFR)

```

## Function Customization

### 1. Model Execution

```{r}
model_execution <- function(data){
    # Create an empty data frame to store the results
  results <- data.frame(PERMNO = character(),
                        Reg5_B1 = numeric(),
                        Reg5_B2 = numeric(),
                        Reg5_P1 = numeric(),
                        Reg5_P2 = numeric(),
                        Reg5_ARS = numeric(),
                        stringsAsFactors = T)
  
  # Loop through all unique company names
  for (company in unique(data$PERMNO)) {
    # Filter the data for the current company
    company_data <- data[data$PERMNO == company,]
    # Create a linear regression model with the constraint on the intercept
    model <- lm(excess_ret ~ 0 + Adj_Market_Ret_Prem + Adj_Sector_Ret_Prem, 
                data = company_data)
  
    # Extract the coefficient values, p-values, and adjusted R-squared
    coefficients <- coef(model)[c("Adj_Market_Ret_Prem", "Adj_Sector_Ret_Prem")]
    p_values <- summary(model)$coefficients[c("Adj_Market_Ret_Prem", "Adj_Sector_Ret_Prem"), "Pr(>|t|)"]
    adjusted_r_squared <- summary(model)$adj.r.squared
  
    # Store the extracted values in the results data frame
    results <- rbind(results, 
                     data.frame(PERMNO = company,
                                Reg5_B1 = coefficients["Adj_Market_Ret_Prem"],
                                Reg5_B2 = coefficients["Adj_Sector_Ret_Prem"],
                                Reg5_P1 = p_values["Adj_Market_Ret_Prem"],
                                Reg5_P2 = p_values["Adj_Sector_Ret_Prem"],
                                Reg5_ARS = adjusted_r_squared,
                                stringsAsFactors = T))
    rownames(results) <- NULL
    
    # Round output to 4 decimal places
    results %<>% 
      mutate_if(is.numeric, round, digits = 4)
  }
  return(results)

}

```

### 2. Statistical Summary

```{r}
statistic_summary <- function(data){
  data %>% 
    select(-PERMNO) %>% 
    describe() %>% 
    select(mean, sd, skew, kurtosis)
}  
```

### 3. Visualization

3.  1 Coefficients

```{r}

density_viz <- function(input, time){
  input %>% 
    select(PERMNO, Reg5_B1, Reg5_B2) %>% 
    gather(key = 'Variable',
           value = 'Coefficient',
           -PERMNO) %>% 
    ggplot(aes(x = Coefficient, fill = Variable)) + 
    geom_density(alpha = 0.5) + 
    labs(title = paste('Density plot of Reg5_B1 and Reg5_B2', time),
         x = "Coefficient",
         y = "Density",
         fill = "Variable") + 
    ylim(c(0,1.15)) + 
    theme_minimal()
}

```

3.  2 Adjusted R-Squared

```{r}

histogram_viz <- function(input, variable, binwdith = 0.05, time){
  input %>%
  ggplot(aes_string(x = variable)) +
  geom_histogram(binwidth = binwdith, fill = "#5DADE2", color = "#2C3E50", alpha = 0.8) +
  labs(title = paste("Distribution of", variable, time),
       x = variable,
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
        axis.title.x = element_text(size = 10, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold"),
        axis.text = element_text(size = 8))
}

```

# Period 1

Extract data for the first period only

```{r}

sample_1 <- full_data %>% 
            filter(year(date) %in% c(2016, 2017, 2018)) %>% 
            select(date, 
                   PERMNO, 
                   excess_ret,
                   Adj_Market_Ret_Prem, 
                   Adj_Sector_Ret_Prem)
```

## Model 5: Excess Return \~ Adjusted Market Returns + Adjusted Sector Returns

### 1. Model's Execution

```{r}
train_1 <- model_execution(sample_1)
```

### 2. Statistical Summary

```{r}
train1_summary <- train_1 %>% 
  statistic_summary()

# train1_summary %>% 
#   write.csv('period1_model_5.csv')
# 
# train_1 %>% 
#   write.csv('Reg5_old_restricted.csv')
```

### 3. Visualization

3.1 Coefficient Viz

```{r}
density_viz(train_1, "From 2016 to 2018")
```

3.2 Adjusted R-Squared

```{r}
histogram_viz(train_1, 
              variable = 'Reg5_ARS',
              time = 'From 2016 to 2018', 
              binwdith = 0.025)
```

# Period 2

Extract data for period 2

```{r}
sample_2 <- full_data %>% 
  filter(year(date) %in% c(2019, 2020, 2021))
```

### 1. Model's Execution

```{r}
train_2 <- model_execution(sample_2)
```

### 2. Statistical Summary

```{r}
train2_summary <- train_2 %>% 
  statistic_summary()

# train2_summary %>% 
#   write.csv('period2_model_5.csv')

# 
# train_2 %>% 
#   write.csv('Reg5_new_resticted.csv')
```

### 3. Visualization

3.1 Coefficient viz

```{r}
density_viz(train_2, 'From 2019 to 2021')
```

3.2 Adjusted R squared

```{r}
histogram_viz(train_2, 
              variable = 'Reg5_ARS',
              time = 'From 2019 to 2021', 
              binwdith = 0.025)
```
