---
`---
title: "Regression 1"
author: "Nam Tran"
format: docx
editor: visual
---

Packages used

```{r}
pacman::p_load(tidyverse, 
               magrittr,
               skimr,
               psych,
               broom)
options(scipen = 999)
```

# Data Preparation

Import the full data to the working environment

```{r}
full_data <- read.csv('full_data.csv', stringsAsFactors = T)
```

Convert PERMNO to factor and format the date column

```{r}
full_data %<>%
  select(-X) %>% 
  mutate(PERMNO = as.factor(PERMNO),
         date = ymd(date)
         )
```

# Period 1

## Function Customization

Extract data for the first period only

```{r}

sample_1 <- full_data %>% 
            filter(year %in% c(2016, 2017, 2018)) %>% 
            select(everything())
```

### 1. Model Execution

```{r}

model_execution <- function(data){
    # Create an empty data frame to store the results
  results <- data.frame(PERMNO = character(),
                        Reg1_B1 = numeric(),
                        Reg1_P1 = numeric(),
                        Reg1_ARS = numeric(),
                        stringsAsFactors = T)
  
  # Loop through all unique company names
  for (company in unique(data[,'PERMNO'])) {
    # Filter the data for the current company
    company_data <- data %>%
      filter(PERMNO == company)
  
    # Create a linear regression model with the constraint on the intercept
    model <- lm(excess_ret ~ 0 + market_prem, 
                data = company_data)
  
    # Extract the coefficient values, p-values, and adjusted R-squared
    coefficient <- coef(model)["market_prem"]
    p_value <- summary(model)$coefficients["market_prem", 
                                           "Pr(>|t|)"]
    adjusted_r_squared <- summary(model)$adj.r.squared
  
    # Store the extracted values in the results data frame
    results <- rbind(results, 
                     data.frame(PERMNO = company,
                                Reg1_B1 = coefficient,
                                Reg1_P1 = p_value,
                                Reg1_ARS = adjusted_r_squared,
                                stringsAsFactors = T))
    rownames(results) <- NULL
    
    # Round output to 4 decimal places
    results %<>% 
      mutate_if(is.numeric, round, digits = 4)
  }
  return(results)

}

```

### 2. Statistical summary

```{r}
statistic_summary <- function(data){
  data %>% 
    select(-PERMNO) %>% 
    describe() %>% 
    select(mean, sd, skew, kurtosis)
}  
```

### 3. Visualization

```{r}
histogram_viz <- function(input, variable, binwdith = 0.05, time){
  input %>%
  ggplot(aes_string(x = variable)) +
  geom_histogram(binwidth = binwdith, fill = "#5DADE2", color = "#2C3E50", alpha = 0.8) +
  labs(title = paste("Distribution of", variable, time),
       x = variable,
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
        axis.title.x = element_text(size = 10, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold"),
        axis.text = element_text(size = 8))
}
```

### 4. Supplying Ticker

```{r}
sup_ticker <- function(dt){
  perm_tick <- (sample_1 %>% 
    select(PERMNO, TICKER) %>% 
    unique())[c(1:357),]
  new_data <- left_join(dt, perm_tick, by = 'PERMNO')
  new_data %<>% 
    select(PERMNO, TICKER, everything())
  return(new_data)
}

```

### 5. Portfolio Beta sorting

-   Sort Beta based on quantile

```{r}
sort_beta <- function(sample_output){
  sample_output$Beta_Type <- cut(sample_output$Reg1_B1, 
    quantile(sample_output$Reg1_B1, 
             probs = c(0, 0.25,0.5, 0.75, 1)),
    labels = c('Low',
               'mid_low',
               'mid_high',
               'high'
               ),
    include.lowest = T)
  
  return(sample_output)
}
```

-   Summarize sorted beta

```{r}
sorted_beta_summary <- function(sample_output){
  summary_output <- sort_beta(sample_output) %>% 
  select(Reg1_B1, Beta_Type) %>% 
  group_by(Beta_Type) %>% 
  summarize(Min = min(Reg1_B1),
            Mean = mean(Reg1_B1),
            Median = median(Reg1_B1),
            Max = max(Reg1_B1)) %>% 
  mutate_if(is.numeric, round, digits = 4)
  
  return(summary_output)
}

```

-   Average Excess return for grouped betas

```{r}
avg_ret_beta_sorted <- function(sample_output, period_data ){
  sample_output$Beta_Type <- cut(sample_output$Reg1_B1, 
    quantile(sample_output$Reg1_B1, 
             probs = c(0, 0.25,0.5, 0.75, 1)),
    labels = c('Low',
               'mid_low',
               'mid_high',
               'high'
               ),
    include.lowest = T)

# Calculate the average excess return for each stock in the sample and group with 
  
  avg_ex_ret <- period_data %>% 
    group_by(PERMNO) %>% 
    summarize('AVG_EX_RET' = mean(excess_ret)) %>% 
    full_join(sample_output, by = 'PERMNO') %>% 
    group_by(Beta_Type) %>% 
    summarize('AVG_EX_RET' = mean(AVG_EX_RET))
  return(avg_ex_ret)
}
```

## Model 1: Stock's Excess Return \~ Unadjusted Market Return

### 1. Model's Execution

```{r}
train_1 <- model_execution(sample_1)


```

### 2. Statistical Summary

```{r}

train_1_summary <- statistic_summary(train_1)

# Export the result
# train_1_summary %>% write.csv('period1_model_1.csv')

# Export the variable's output

# train_1 %>% 
#   write.csv('Reg1_old_restricted.csv')

```

### 3. Visualization

```{r}
histogram_viz(train_1, 
              variable = 'Reg1_B1',
              time = 'from 2016 to 2018')
```

```{r}
histogram_viz(train_1, variable = 'Reg1_ARS', 
              binwdith = 0.015,
              time = 'from 2016 to 2018')
```

### 4. Extract data with PERMNO and Tickers

```{r}
train_1 %<>% 
  sup_ticker()
```

### 5. Portfolio Sorting based on Betas

```{r}

avg_ex_ret_beta_1 <- avg_ret_beta_sorted(train_1, sample_1)

summary_beta_output_1 <- sorted_beta_summary(train_1)
```

# Period 2

Change the sub sample dataset

```{r}
sample_2 <- full_data %>% 
  filter(year(date) %in% c(2019, 2020, 2021))
```

## Model 1: Stock's Excess return \~ Market Premium

### 1. Model's Execution

```{r}
validation_1 <- model_execution(sample_2)
```

### 2. Statistical Summary

```{r}
valid_1_summary <- statistic_summary(validation_1)

# Export Summary
# valid_1_summary %>% write.csv('period2_model_1.csv')

# Export variable's outputs
# 
# validation_1 %>% 
#   write.csv('Reg1_new_restricted.csv')
```

### 3. Visualization

```{r}
histogram_viz(validation_1, 
              variable = 'Reg1_B1', 
              time = 'From 2019 to 2021')
```

```{r}
histogram_viz(validation_1, 'Reg1_ARS', 
              binwdith = 0.015,
              'From 2019 to 2021')
```

### 4. Extract stocks with Tickers

```{r}
low_beta_2 <- sup_ticker(validation_1) %>% 
  filter(Reg1_B1<1)
```

### 5. Porfolio Sorting based on beta

```{r}
avg_ex_ret_beta_2 <- avg_ret_beta_sorted(validation_1, sample_2)


summary_beta_output_2 <- sorted_beta_summary(validation_1)

```

```{r}

```
